\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-16 paper.tex
typo

Following this work, we investigate custom-fit, in-ear EEG earpieces as a platform for one-step, three-factor authentication.
We use the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor 3).
 %% In addition to the dual knowledge and inherence factors established in previous work, this study incorporates a possession factor in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in their ear. These earpieces can serve as physical tokens in the same way as bank ATM cards and wearable hardware tokens by implementing a hardware key-pair.
 %% Furthermore, because the earpieces are custom-fitted to each individual, we predicted they would likely not be able to produce good electrical impedances when worn by a different individual.
%% Because three-factor authentication (3FA) requires the user to submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security possible. The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is a promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user.

>>>>

Following this work, we investigate custom-fit, in-ear EEG earpieces as a platform for one-step, three-factor authentication.
We use the choice of a mental task or "passthought" to perform as knowledge (factor one), the uniqueness of an individual's brain activity as measured by EEG as inherence (factor two), and the physical token of custom-fit earpieces, which could easily contain a hardware key-pair, as a possession factor (factor three).
 %% In addition to the dual knowledge and inherence factors established in previous work, this study incorporates a possession factor in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in their ear. These earpieces can serve as physical tokens in the same way as bank ATM cards and wearable hardware tokens by implementing a hardware key-pair.
 %% Furthermore, because the earpieces are custom-fitted to each individual, we predicted they would likely not be able to produce good electrical impedances when worn by a different individual.
%% Because three-factor authentication (3FA) requires the user to submit one distinct instance of each type of authenticator, it represents the strongest level of authentication security possible. The ability to utilize all three of these security factors in a single step by performing a mental task of a few seconds is a promising in pursuit of extremely strong security while maintaining a low amount of effort and obtrusiveness to the user.
